Open archaeology, open source?

### 2024-01-27 analysis/_04-open_archaeology.qmd
Resolve TODOs in section 4

```{r num-p_platform_r}
p_platform_r <- sum(oarch$platform == "R", na.rm = TRUE) / nrow(oarch)
```

`r percent(p_platform_r)` of projects are extensions to the statistical programming language R, making it the most widely-used platform by a large margin (@tbl-platforms).
Python, another programming language, is also relatively popular <!-- TODO: percent -->, as are plugins for the open source geographic information system QGIS <!-- TODO: percent -->.
Beyond that, there is a rather fragmented landscape of plugins for other desktop software (e.g. AutoCAD, ArcGIS), a number of lesser used programming languages, and a genre consisting of custom forms and spreadsheet templates.
Many of these are targeted by only one or two developers; the larger platforms tend to be more diverse.

@@

<!-- TODO: can we say anything more concrete about the tags? 
ZB response: We can look at the development of tags over time. For instance, a chart documenting year-over-year growth of each tag based on date of each project's first commit. I imagine this as a stacked bar chart (similar to below) but with segments coded to represent year of first commit. This would fit at the end of this section, under fog-github-cumulative. We can add charts documenting growth of platforms and licenses too. -->

>>>>

```{r num-p_platform_r}
p_platform_r <- sum(oarch$platform == "R", na.rm = TRUE) / nrow(oarch)
p_platform_python <- sum(oarch$platform == "Python", na.rm = TRUE) / nrow(oarch)
p_platform_qgis <- sum(oarch$platform == "QGIS", na.rm = TRUE) / nrow(oarch)
```

`r percent(p_platform_r)` of projects are extensions to the statistical programming language R, making it the most widely-used platform by a large margin (@tbl-platforms).
Python, another programming language, is also relatively popular (`r percent(p_platform_python)`), as are plugins for the open source geographic information system QGIS (`r percent(p_platform_qgis)`).
Beyond that, there is a rather fragmented landscape of plugins for other desktop software (e.g. AutoCAD, ArcGIS), a number of lesser used programming languages, and a genre consisting of custom forms and spreadsheet templates.
Many of these are targeted by only one or two developers; the larger platforms tend to be more diverse.

@@
